\cvsection{Projects}
\vspace{-0.1cm}

\begin{cvprojects}

%---------------------------------------------------------
\cvproject
    {\href{https://github.com/kaihulme/ad-gan}{\faGithubSquare\acvHeaderIconSep ad-gan}} % Project location
    {GANs for Alzheimer's Disease Detection} % Project Name
    {\begin{cvitems}
        \item Thesis project studying the use of GANs as an augmentation technique for improved Alzheimer’s Disease detection in MRI volumes.
        \item Using the OASIS dataset of Alzheimer's Disease patients, built neuroimaging pre-processing pipelines with NiPype to use data with ML models.
        \item Built a method for Alzheimer's Disease classification in MRI volumes using a slice extraction method and CNN model using TensorFlow / Keras.
        \item Implementation of Generative Adversarial Networks in TensorFlow / Keras with custom training logic and loss functions.
        \item Implementation of current literature on GAN models and machine learning Alzheimer's Disease detection methods.
        \item Model deployment to Nvidia GPU using Docker containerisation.
      \end{cvitems}
    }
    
%---------------------------------------------------------
\cvproject
    {\href{https://github.com/kaihulme/alspac-mhst}{\faGithubSquare\acvHeaderIconSep alspac-mhst}} % Project location
    {Mental Health and Screen Time} % Project Name
    {\begin{cvitems}
        \item Data science team project for Jean Golding Institute, analysing ALSPAC data for correlation of screen usage and child mental health issues.
        \item Mostly missing data led to analysis of various developed multivariate model-based imputation methods using Scikit-Learn and XGBoost.
        \item Using classification methods and statistical analysis it was concluded, given the data, there was little to no evidence for such a correlation.
        \item IEEE paper with full analysis and methods available on GitHub repository.
      \end{cvitems}
    }
    
%---------------------------------------------------------
\cvproject
    {\href{https://github.com/kaihulme/ml-analysis}{\faGithubSquare\acvHeaderIconSep ml-analysis}} % Project location
    {Machine Learning Model Analysis} % Project Name
    {\begin{cvitems}
        \item Analysis and optimisation of various classification and regression models using Scikit-Learn, Keras and PyMC3.
        \item Built visualisation and performance methods to compare support vector machines, neural networks and ensemble classification models.
        \item Implemented Bayesian linear regression with PyMC3 to embed prior domain knowledge into the model learnt during exploratory data analysis.
        \item Built Scikit-Learn wrapper around PyMC3 regression model for comparison of Bayesian and frequentist regression methods.
      \end{cvitems}
    }
    
%---------------------------------------------------------
\cvproject
    {\href{https://github.com/kaihulme/dartboard-detection}{\faGithubSquare\acvHeaderIconSep dartboard-detection}} % Project location
    {Dartboard Detection} % Project Name
    {\begin{cvitems}
        \item {Dartboard detection using OpenCV and traditional computer vision techniques implemented in C++ and Python.}
        \item {Bounding box detection from images using ensemble of Viola-Jones cascades, Hough transform shape detectors and KMeans clustering.}
      \end{cvitems}
    }
    
% %---------------------------------------------------------
% \cvproject
%     {\href{https://github.com/kaihulme/os-kernel}{\faGithubSquare\acvHeaderIconSep os-kernel}} % Project location
%     {Operating System Kernel} % Project Name
%     {\begin{cvitems}
%         \item {Point 1.}
%         \item {Point 2.}
%       \end{cvitems}
%     }
    
% %---------------------------------------------------------
% \cvproject
%     {{\href{https://github.com/kaihulme/game-of-life}{\faGithubSquare\acvHeaderIconSep game-of-life}}} % Project location
%     {Game of Life} % Project Name
%     {\begin{cvitems}
%         \item {Point 1.}
%         \item {Point 2.}
%       \end{cvitems}
%     }

%---------------------------------------------------------

\end{cvprojects}
