\cvsection{Work Experience}
\vspace{-0.1cm}

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Project Mentor and Teaching Assistant} % Job title
    {University of Bristol, Computer Science Department} % Organization
    {Bristol} % Location
    {Sep 2019 - Jun 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Mentoring groups of students on their software engineering projects, providing feedback to professors and teaching assistance in coding labs.
        \item Evaluated progress through weekly meetings; giving technical and peer advice, resolving issues and ensuring they meet release requirements.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Supervisor} % Job title
    {Kongs of King Street} % Organization
    {Bristol} % Location
    {Sep 2017 - Jan 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Working in busy bar in Bristol alongside my studies; promoted to supervisor role which saw me supervise a team of 10+ staff each weekend.
        \item Responsible for opening and closing the bar, managing mine and others time under stress and ensuring the team is working together effectively.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer and Team Lead for university project} % Job title
    {BioScientifica} % Organization
    {Bristol} % Location
    {Sep 2018 - May 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Full software product and portfolio for client at BioScientifica, with successful trial-run held at SfE BES 2019.
        \item Android application to gamify events with QR code treasure hunt quiz, targeted at early career clinicians and monitored by a team of experts.
        \item Developed using agile and test-driven methodologies with version control and CI/CD using Git and CircleCI.
        \item Full stack development of Java web app to create and monitor events with API for communication to MySQL database hosted with AWS.
        \item Showing strong team management and leadership skills, I was put forward to mentor teams of students with their projects the following year.
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
