\cvsection{Work Experience}
\vspace{-0.1cm}

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Project Mentor and Teaching Assistant} % Job title
    {University of Bristol, Computer Science Department} % Organization
    {Bristol} % Location
    {Sep 2019 - Jun 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Mentoring groups of students on their software engineering projects, providing feedback to professors and teaching assistance in coding labs.
        \item Evaluated progress through weekly meetings; giving technical and peer advice, resolving issues and helping meet their release schedule.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Supervisor} % Job title
    {Kongs of King Street} % Organization
    {Bristol} % Location
    {Sep 2017 - Jan 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Working in busy bar in Bristol alongside my studies; promoted to supervisor role which saw me supervise a team of 10+ staff each weekend.
        \item Managed mine and others time, ensured the team works together effectively during busy periods and increased efficiency.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer (through UoB project)} % Job title
    {BioScientifica} % Organization
    {Bristol} % Location
    {Sep 2018 - May 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Team lead for full software product and portfolio for client at BioScientifica, with successful trial-run held at SfE BES 2019.
        \item Full stack development of Spring Boot Java web app and REST API, hosted in AWS with MySQL database.
        \item Utilised agile and test-driven development, building CI/CD pipelines with CircleCI and managing my team through GitHub and Jira.
        \item Showing strong team management and leadership skills, I was put forward to mentor project teams the following year.
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
